---
title: "Tatiana_Activity1"
author: "Tatiana Ferrari"
date: "20/09/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Research Interest

My mainly research interested is in the ways to promote the changing of the actuall urban mobility pattern (based on car) to a more **sustainable urban transportation** pattern. This envolves a huge field of research and to go more straight I`m interested in understand how the **urban form**, the design of the built environment can control and shape the **individual’s travel behavior**. Although the numerous researches relating the urban form and travel behavior, some of these results are still questioned, and investigation about the *degree of this influence in relation to sociodemographic characteristics* and which *aspects of urban form are relevant* are still needed. In addition, the theoretical contributions established in the literature are based in studies carried out mainly in the developed countries. There is a lack of empirical work on the subject in **developing countries**, which has different spatial dynamics that could bring other issues to the debate.


# Favorites 

## Favorite Music

1. Rebirth - Angra
2. Triste, Louca ou Ma - Francisco el Hombre
3. Vocalise - Rachmaninoff 
4. #41 - Dave Matthews Band
5. Telegrama - Zeca Baleiro

## Favorite Equation

I say as my favorite equation the fundamental theorem of calculus. It`s a important equation, since forms the backbone of the mathematical method known as calculus, and relates differentiation and integration. The theorem simply states that the sum of infinitesimal changes in a quantity over time is equal to the integral of the rate of change of that quantity.

$\int_{a}^{b} f'(x)dx = f(b) - f(a)$


## Favorite Artists 

| Name        | Achievements |
| ------------- |:-------------:| -----:|
| Uğur Gallenkuş  | He is an Turkish artist that works with photographers collages. The photos are justaposed in a cleverly way that shocks and make us think about of the world we live in. |
| Tarsila do Amaral  | She is considered one of the leading Latin American modernist artists, described as the Brazilian painter who best achieved Brazilian aspirations for nationalistic expression in a modern style.|
|Itzhak Perlman     | One of the greastest violin players of our times. |
|Salvador Dalí | He was a famous Spanish painter. He's works has melting watches and eerie blasted landscapes, Dalí’s paintings were the epitome of Surrealism. |
| Ricardo Darín    | An Argentine actor, screenwriter and film director. He has performed very well in several films such as: The Secret in their eyes; Truman; Chinese Take-Away; White Elephant.|

# A Chunk of Code

To insert a chunck code quickly press: __Ctrl+Alt+I__

``` {r include=TRUE}
library(praise)

praise("${EXCLAMATION}! You have done this ${adjective}!")

```


